\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{parskip}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

\pagestyle{fancy}
\fancyhf{}
\rhead{Project Selection Tool}
\rfoot{Page \thepage}
\renewcommand{\headrulewidth}{0.4pt}

\title{\textbf{Project Selection Tool}\\[0.5em]\large Setup Guide}
\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{fancy}

\section*{Step 1: Create Your Product List}

\begin{enumerate}[leftmargin=*]
    \item Go to \href{https://sheets.google.com}{sheets.google.com}
    \item Click \textbf{Blank} to create a new spreadsheet
    \item Name it something like ``Product Selections''
\end{enumerate}

\subsection*{Set Up Your Columns}

In the first row, add these headers:

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Column A} & \textbf{Column B} \\
\midrule
category & name \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Add Your Products}

Add one product per row. The \textbf{category} column determines which step it appears in.

\textbf{Example:}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{category} & \textbf{name} \\
\midrule
Vanity & 36" White Shaker \\
Vanity & 48" Gray Flat Panel \\
Vanity & 60" Espresso \\
Countertop & White Quartz 2cm \\
Countertop & Gray Granite 3cm \\
Sink & White Undermount Rectangle \\
Sink & Biscuit Vessel Oval \\
Faucet & Chrome Single Handle \\
Faucet & Brushed Nickel Widespread \\
\bottomrule
\end{tabular}
\end{center}

The order of categories in your sheet = the order of steps in the app.

\newpage

\section*{Step 2: Publish Your Sheet}

\begin{enumerate}[leftmargin=*]
    \item In Google Sheets, go to \textbf{File $\rightarrow$ Share $\rightarrow$ Publish to web}
    \item In the first dropdown, select your sheet name (or ``Entire document'')
    \item In the second dropdown, change ``Web page'' to \textbf{``Comma-separated values (.csv)''}
    \item Click the green \textbf{Publish} button
    \item Click \textbf{OK} on the popup
    \item \textbf{Copy the URL} that appears
\end{enumerate}

The URL will look something like:

\begin{center}
\texttt{https://docs.google.com/spreadsheets/d/e/2PACX.../pub?output=csv}
\end{center}

\section*{Step 3: Connect to the App}

\begin{enumerate}[leftmargin=*]
    \item Open the app: \textbf{\underline{\hspace{6cm}}} {\small (URL provided separately)}
    \item Paste your Google Sheets URL in the box
    \item Click \textbf{Save \& Continue}
\end{enumerate}

Done! Your products now appear in the selection wizard.

\section*{Updating Products}

To add, remove, or edit products:

\begin{enumerate}[leftmargin=*]
    \item Just edit your Google Sheet (add rows, change names, etc.)
    \item Changes are automatic---users just need to refresh the page
\end{enumerate}

\textbf{No need to republish.} Edit the sheet anytime.

\section*{Tips}

\begin{itemize}[leftmargin=*]
    \item Keep category names consistent (capitalization matters)
    \item Add new categories by just typing a new category name
    \item The app steps through categories in the order they first appear
    \item You can add extra columns (like ``price'' or ``notes'')---they won't break anything
\end{itemize}

\vfill

\begin{center}
\rule{0.5\textwidth}{0.4pt}\\[1em]
\textbf{Questions?} Contact: \underline{\hspace{5cm}}
\end{center}

\end{document}
